### 2023-03-17 notebooks/fidelity.qmd
penalty working

```{julia}
# Setup
counterfactual_data = load_multi_class()
M = fit_model(counterfactual_data, :MLP)
target = 4
factual = 1
chosen = rand(findall(predict_label(M, counterfactual_data) .== factual))
x = select_factual(counterfactual_data, chosen)
```

```{julia}
niter = 10
nsamples = 100
plts = []
for target in ce.data.y_levels
    # Search:
    generator = GenericGenerator()
    ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
    sampler = CCE.EnergySampler(ce;niter=niter, nsamples=100)
    Xgen = rand(sampler, nsamples)
    plt = plot(M, counterfactual_data, target=ce.target, xlims=(-5,5),ylims=(-5,5),cbar=false)
    scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
    push!(plts, plt)
end
plot(plts..., layout=(1,length(ce.data.y_levels)), size=(length(ce.data.y_levels)*300,300))
```

>>>>

```{julia}
# Setup
counterfactual_data = load_multi_class()
M = fit_model(counterfactual_data, :MLP)
target = 4
factual = 2
chosen = rand(findall(predict_label(M, counterfactual_data) .== factual))
x = select_factual(counterfactual_data, chosen)

# Search:
generator = GenericGenerator(opt=Descent(0.01))
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
```

```{julia}
niter = 100
nsamples = 100

sampler = CCE.EnergySampler(ce;niter=niter, nsamples=100)
Xgen = rand(sampler, nsamples)
plt = plot(M, counterfactual_data, target=ce.target, xlims=(-5,5),ylims=(-5,5),cbar=false)
scatter!(Xgen[1,:],Xgen[2,:],alpha=0.5,color=target,shape=:star,label="X|y=$target")
```

```{julia}
p1 = plot(ce)
```

```{julia}
@objective(generator, _ + 0.1distance_l2 + 100.0distance_from_energy)
ce = generate_counterfactual(x, target, counterfactual_data, M, generator)
p2 = plot(ce)
```
